\section{GEM based Readout}
\label{chap:TPC_sec:standard_gems}

Gas Electron Multipliers (GEMs) \cite{Sauli1997531} have been invented in the mid 90's. They consist of a thin polyamide foil, covered with Copper on both sides. Holes are produced into the foil on a regular pattern. Typical dimensions are a hole pitch of \SI{140}{\micro m} and a hole diameter of \SI{70}{\micro m}. If an electric field is applied between the two sides of the foil, high fields form inside the holes, and provide avalanche gas amplification. Since the high fields are constrained inside the holes, many of the high-voltage problems connected to traditional wire based chambers are not relevant. GEM foils can be stacked to provide tailored gas amplification. During the years a number of different types of GEM foils have been developed. They differ for example in the cross section of the holes, in the material of the foil, and in the pitch and hole sizes. For application in the ILC TPC currently two main options are being pursued. The first one is based on a GEM where a laser is used to ``drill'' each hole.
The resulting holes are
strictly cylindrical. The second option is based on a chemical etching process. The resulting holes have a double conical shape.

In addition to the different types of GEM foils two different schemes to build readout modules for the TPC are investigated. Scheme one (called module type A in the following) relies on a sturdy aluminum frame where the GEM foils are stretched between the bottom and the top of the readout module. This scheme allows to build a module which has essentially no dead area on the side of the module, but where some dead space is needed on the top and the bottom. The second option (called module type B in the following) relies on an assembly of a stiff but thin ceramic frame which when glued to the GEM provides a self-supporting stiff assembly. The width of the frame is around one millimeter, so that in this approach a small dead area is present all around the module. Both approaches allow the stacking of GEM foils, and both are compatible with the installation of a gating GEM on top.

\input{Tracker/TPC_Bonn/asian_gems}
\input{Tracker/TPC_Bonn/standard_gems}
